---
title: "2019 Canadian Federal Election Analysis by MRP model"
author: "Ligeng"
date: "21-DEC-2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
urlcolor: blue
fontsize: 12pt
abstract: This report is mainly focus on identify how the 2019 Canadian Federal Election
  would have been different if ‘everyone’ had voted. A Multilevel regression (MRP)
  model will be built based on the data from Canadian Election Study (CES). There
  are only 37,822 cases from 2019 CES data, as a result, a national census data will
  be collected as post-stratification dataset. Apply selected Multilevel regression
  model on post-stratification dataset to see whether predicted election result is
  different from actual election result
bibliography: Reference.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

__keywords__: "Election, MRP, CES, Post-stratification, Multilevel, Logistic Regression, Prediction, Vote, Prime Minister"


__Git Website:__ (https://github.com/Gengli8098/STA304_final)


\newpage


\section{Introduction}

2019 Canadian election was the $43^{rd}$ Canadian general election, which was held on October 21, 2019. The liberty Party led by Justin Trudeau won 157 seats to form a minority government [@Wikipedia]. At the same time, 2019 Canadian Election Study (CES2019) conducted an online survey, this survey was composed by Pre-election survey and Post-election survey in different time period. Target population of survey is Canadian citizens and permanent residents, aged 18 or older [@CES]. There are 620 variables in CES2019 data. However, it is impossible to use all variables in this analysis, we will pick up some of them, which are representative to elections to do a meaningful statistical analysis.  

In this project, we want to identify differences if more people were get involved in 2019 elections. The statistical method we are going to use is MRP based on CES2019 and Canada Census dataset. In the CES2019 dataset, there are several variables that indicates individual's ratings to different parties, that means for party that got the highest rating had the largest possibility to win the election. As a result, our multilevel regression model will explain relationship between parties' ratings and other predictors (e.g. education, gender and etc.).  

Further, we will apply multilevel regression model that was obtained based on CES2019 data to post-stratification data to see whether parties rating will change if more and more people in Canada get involved in election.  

In the next few sections, we will start from introducing CES2019 and post-stratification datasets by doing some data analysis. Next, we will introduce specific multilevel regression model and how to apply it to post-stratification dataset. Moreover, we will present data analysis and regression model results. Finally, we will discuss outputs including project summary and project limitations. 


\newpage


\section{Method and Methodology}

This section mainly describes methods and methodologies that will be applied in the rest of data analysis. Methods and methodologies about datasets and model will be introduced in the next two sub sections.

\subsection{Data Descriptions}

In this project, there are two datasets that are mainly analyzed. The first one is Canadian Election Study (CES) online data in 2019. CES data is response collection of 2019 Canadian Election survey, population of this survey is all Canadian Citizen in 2019 [@CES]. CES online data has two parts: Campaign Period Survey which happened before election and Post-election survey which happened after election. In the original online CES dataset, there are 37822 observations and only 10340 observations belong to Post-election survey [@CES]. In this report, 10340 observations belong to Post-election survey will be investigated because 'leader rating' from post-election survey will be used to determine whether Justin, Trudeau was selected or not. 'Leader Rating' is ranged from 1 to 10, '1' means really dislike and '10 ' means really like [@CES]. Below data summary of selected variables from original CES dataset after some variable transformation. Below is data summary of CES dataset after some cleaning and transformation, _'Support_Trudeau'_ is response variable which is determined by Trudeau's ratings: if his rating was greater than 5 then setting _'Support_Trudeau'_ to be 1 and 0 otherwise. The rest of variables are all predictors.  



```{r,eval = TRUE, echo=FALSE, warning=FALSE, message=FALSE}

### Required Library ### 

library(haven)
library(tidyverse)
library(knitr)
library(skimr)


# Read in the raw data (You might need to change this if you use a different dataset)
raw_data <- read_dta("2019 Canadian Election Study - Online Survey v1.0.dta")

CES_data <- raw_data %>% select(pes19_lead_rate_8, cps19_province, cps19_citizenship, 
                                cps19_gender, cps19_age) %>%
  rename(Support_Trudeau = pes19_lead_rate_8, province = cps19_province,
         citizenship = cps19_citizenship,
         gender = cps19_gender, age = cps19_age)  %>% 
  filter(Support_Trudeau != 'NA') %>%
  mutate(Support_Trudeau = ifelse(Support_Trudeau > 5, '1', '0'),
         province = case_when(province == 14 ~ 'Alberta', province == 15 ~'British Columbia',
                   province == 16 ~ 'Manitoba', province == 17 ~  'New Brunswick',
                   province == 18 ~ 'Newfoundland and Labrador',
                   province == 19 ~'Northwest Territories',
                   province == 20 ~ 'Nova Scotia', province == 21 ~  'Nunavut', 
                   province == 22 ~'Ontario',
                   province == 23 ~ 'Prince Edward Island', province == 24 ~  'Quebec', 
                   province == 25 ~ 'Saskatchewan', province == 26 ~ 'Yukon'
                   ),
         citizenship = case_when(citizenship == 4~'Citizen', citizenship == 5~'PR',
                                 citizenship == 6~'Other'),
         gender = case_when(gender == 1~'Man', gender == 2~'Woman',
                                 gender == 3 ~ 'Other'),
         age = case_when(age <=25 ~ 'Young People', age <= 50 ~ 'Adult People', 
                         age <= 75 ~ 'Senior People', age > 75 ~ 'Old People')
         )


CES_data$province <- as.factor(CES_data$province)
CES_data$citizenship <- as.factor(CES_data$citizenship)
CES_data$gender <- as.factor(CES_data$gender)

skim(CES_data)

```


\newpage


The second dataset is from Canadian General Social Survey [@GSS]. It contains all predictors in the Multi-Level Logistic Regression Model fitted based on CES dataset above. It will be used as a post-stratification dataset. Same as CES dataset, GSS data will be cleaned and transformed by _"gss_cleaning"_ module (provided in problem set 2 package - Appendix). Below is summary of Canadian General Social Survey dataset.  

```{r,eval = TRUE, echo=FALSE, warning=FALSE, message=FALSE}
GSS_full <- read.csv('gss.csv')

data.frame('Number of Variables' = 81, 'Number of Observations' = 20597,
                  'Key Variables' = 'age, province, citizenship_status, is_male') %>% kable()

GSS <- GSS_full %>% select(province, age, citizenship_status, is_male) %>%
  rename(province = province, age = age, gender = is_male, citizenship = citizenship_status) %>%
  filter(citizenship != 'NA', citizenship != "Don't know") %>%
  mutate(
         age = case_when(age <=25 ~ 'Young People', age <= 50 ~ 'Adult People', 
                         age <= 75 ~ 'Senior People', age > 75 ~ 'Old People'),
         citizenship = case_when(citizenship == 'By birth'~ 'Citizen',
                                 citizenship == 'By naturalization'~ 'PR'),
         gender = case_when(gender == 1 ~ 'Man',
                            gender == 0 ~ 'Woman')
         )


GSS$province <- as.factor(GSS$province)
GSS$citizenship <- as.factor(GSS$citizenship)
GSS$gender <- as.factor(GSS$gender)
GSS$age <- as.factor(GSS$age)

skim(GSS)

```



\subsection{Model Descriptions}

In order to investigate impact of election if 'everyone' had voted in Canada. Multi-Level Regression Model will be built based on CES dataset and apply to post-stratification data set. _'Support_Trudeau (Y)'_ is a binary variable (e.g. '1' represents for support Trudeau and '0' otherwise), as a result, we will Create a random intercept logistic model for full Bayesian inference. Model's mathematical notation is [@MRP]:

$$log(\frac{Y}{1-Y})=\beta_0+\beta_1*citizenship+\beta_2*gender+\beta_3*age+(1\ |\ province)$$

And post-stratification outcome will be computed mathematically as follows, where $\hat{Y_j}$ is predicted value for each group, $N_j$ is size of each group.  

$$\hat{Y}^{PS}=\frac{\sum\limits_{j=1}^nN_j\hat{Y_j}}{\sum\limits_{j=1}N_j}$$


\newpage


\section{Results}

In this section, CES data analysis results and model outputs will be shown and interpreted.


\subsection{CES data Analysis}

```{r,eval = TRUE, echo=FALSE, warning=FALSE, message=FALSE,fig.width=20, fig.height=10}
library(ggplot2)
library(gridExtra)

Citizenship <- CES_data %>% group_by(citizenship) %>% 
  summarise(Support_Trudeau_Percent=sum(as.integer(Support_Trudeau))/n()) %>%
  ggplot(aes(x=citizenship, y=Support_Trudeau_Percent, color=citizenship)) +
  geom_bar(stat="identity", fill="white")+theme_bw() + labs(title="Trudeau Support Percentage By Citizenship") +   theme(
    axis.text.x = element_text(size=30),
          axis.text.y = element_text(size=30),
          axis.title = element_text(face="bold", size = 400),
          axis.title.x = element_text(size = 30),
          axis.title.y = element_text(size = 30),
    plot.margin = unit(c(3,3,3,3),"cm")) + theme_classic()

Gender <- CES_data %>% group_by(gender) %>% 
  summarise(Support_Trudeau_Percent=sum(as.integer(Support_Trudeau))/n()) %>%
  ggplot(aes(x=gender, y=Support_Trudeau_Percent, color=gender)) +
  geom_bar(stat="identity", fill="white")+theme_bw() + labs(title="Trudeau Support Percentage By Gender") +   theme(
    axis.text.x = element_text(size=30),
          axis.text.y = element_text(size=30),
          axis.title = element_text(face="bold", size = 400),
          axis.title.x = element_text(size = 30),
          axis.title.y = element_text(size = 30),
    plot.margin = unit(c(3,3,3,3),"cm")) + theme_classic()

province <- CES_data %>% group_by(province) %>% 
  summarise(Support_Trudeau_Percent=sum(as.integer(Support_Trudeau))/n()) %>%
  ggplot(aes(x=province, y=Support_Trudeau_Percent, color=province)) +
  geom_bar(stat="identity", fill="white")+theme_bw() + labs(title="Trudeau Support Percentage By Province") +   theme(
    axis.text.x = element_text(size=30),
          axis.text.y = element_text(size=30),
          axis.title = element_text(face="bold", size = 400),
          axis.title.x = element_text(size = 30),
          axis.title.y = element_text(size = 30),
    plot.margin = unit(c(3,3,3,3),"cm")) + theme_classic()

age <- CES_data %>% group_by(age) %>% 
  summarise(Support_Trudeau_Percent=sum(as.integer(Support_Trudeau))/n()) %>%
  ggplot(aes(x=age, y=Support_Trudeau_Percent, color=age)) +
  geom_bar(stat="identity", fill="white")+theme_bw() + labs(title="Trudeau Support Percentage By Age") +   theme(
    axis.text.x = element_text(size=30),
          axis.text.y = element_text(size=30),
          axis.title = element_text(face="bold", size = 400),
          axis.title.x = element_text(size = 30),
          axis.title.y = element_text(size = 30),
    plot.margin = unit(c(3,3,3,3),"cm")) + theme_classic()


grid.arrange(Citizenship, Gender, province, age)
```

  

\subsection{Model Analysis}

Below are results from full Bayesian inference Multi-level Logistic Regression model by controlling province.  

```{r,eval = TRUE, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
library(broom) # Helps make the regression results tidier
library(tidyverse) # Helps make programming with R easier
library(brms)

full <- brm(Support_Trudeau ~ gender + citizenship + age + (1|province),
              data = CES_data, 
              family = bernoulli())
```

```{r,eval = TRUE, echo=FALSE, warning=FALSE, message=FALSE}
summary(full)
```



Before applying MRP model to post-stratification dataset, we calculate population percentage within each group, because we need to apply this percentage into predicted value in each cell. Below are percentage for first few groups - full list of percentage will be presented in the appendix. For example, proportion of group (Male Adult citizen) in Alberta is 16% percent and 2% for old Adult citizen and etc.


```{r,eval = TRUE, echo=FALSE, warning=FALSE, message=FALSE}
GSS_Group <- GSS %>% group_by(province, gender, citizenship, age) %>%
  summarise(Total_Population = n()) %>%
  group_by(province) %>% mutate(Population_Percent = Total_Population/sum(Total_Population))

GSS_SUMM <- head(GSS_Group) %>% kable(caption = "Proportion of Population in Each Cell (First 6 groups)")

```

```{r,eval = TRUE, echo=FALSE, warning=FALSE, message=FALSE}

POST <- full %>%
tidybayes::add_predicted_draws(newdata =GSS_Group) %>%
rename(alp_predict =.prediction) %>%
mutate(alp_predict_prop =alp_predict*Population_Percent) %>%
group_by(province, .draw) %>%
summarise(alp_predict =sum(alp_predict_prop)) %>%
group_by(province) %>% 
summarise(Average_Vote_Trudeau = mean(alp_predict),
          lower_bound =quantile(alp_predict,0.025),
          upper_bound =quantile(alp_predict,0.975)) %>%
  kable(caption = "Predicted Percentage of Supporting Justin, Trudeau ('Everyone' voted)")

Actual <- CES_data %>% group_by(province) %>% 
  summarise(Support_Trudeau_Percent=sum(as.integer(Support_Trudeau))/n()) %>%
  kable(caption = "Actual Percentage of Supporting Justin, Trudeau in 2019")

GSS_SUMM
POST
Actual
```

Above two tables are "Actual Percentage of Supporting Justin, Trudeau in 2019" compared with "Predicted Percentage of Supporting Justin, Trudeau if 'everyone' voted".  


\newpage


\section{Discussion}


\subsection{Summary}

MRP modeling was done until now in the modeling ad methodology section. First of all, Canadian Election Study dataset in 2019 was downloaded and used to fit Bayesian Multi-level logistic regression model, which was interpreted in above section. Second of all, Canadian General Social Survey dataset was downloaded and transformed as post-stratification data. Thirdly, apply fitted Multi-level logistic regression model to post-stratification data to predict the impact of 2019 election if 'everyone' voted.   

\subsection{Conclusion}

Firstly, from 2019 Canadian Election online data analysis results (Plots in Results Section), we can find:  

  * Trudeau got higher supports from Permanent Resident (70%) compare to Citizen (50%). However, permanent resident has much less population than citizen.  
  
  * Trudeau got higher supports from Women (more than 50%) compare to Men (43%) and Other (49%).  
  * Trudeau got higher supports from Yukon, but Yukon has only one voter in sample data. Except Yukon, Trudeau got highest supports from Nova Scotia (50%).
  
  * Trudeau got approximately equal supports from different age groups, but younger people group has higher support rate to Trudeau.  

Secondly, from Bayesian Multi-level logistic regression model summary, it tells coefficient estimation of each predictors. For example: Log odds of supporting Trudeau is 0.42 from woman, Log odds of supporting Trudeau is 0.46 from permanent resident, Log odds of supporting Trudeau is 23 from people over 75 years old and etc. 

Finally, after applying Bayesian Multi-level logistic regression model to post-stratification dataset. By comparing two tables: "Actual Percentage of Supporting Justin, Trudeau in 2019" compared with "Predicted Percentage of Supporting Justin, Trudeau if 'everyone' voted". We can tell that total predicted support rate to Trudeau is little bit higher than his actual support rate in 2019. However, _'Prince Edward Island Province'_ has lower support rate to Trudeau.  




\subsection{Weakness and Next Steps}

All data and model analysis was finalized. However, few weaknesses were identified during modeling process. In this part, weaknesses and corresponding proposed solutions are addressed in order to make this analysis more accurate and less biases.  

  * In the Canadian Election Study dataset, Trudeau's support indicator is determined by his 'leader rating' ranged from 1 to 10, when his leader rating is greater than 5, then support Trudeau's indicator is 1. This classification must cause some biases because for people who gave him high leader rating doesn't mean give him a vote.  
  
  Further steps: for reducing biases, more variables should be collected post election, including voters' actual voting.  
  
  * After fitting logistic regression model, model diagnostics were not processed, because model diagnostics tell whether logistic regression model need to be improved (e.g. variable transformation, outlier/leverage points removal and etc.).   
  
  Further steps: diagnose Multi-Level logistic regression model to check whether all model assumptions are satisfied. If some model assumptions are not satisfied, then data and model should be cleaned and refitted.
  
  

\section{Reference} 

<div id="refs"></div>


\newpage


\section{Appendix} 

```{r, eval = FALSE, echo=TRUE}
# Load the data dictionary and the raw data and correct the variable names
raw_data <- read_csv("AA8MGinv.csv")
dict <- read_lines("gss_dict.txt", skip = 18) # skip is because of preamble content
# Now we need the labels because these are the actual responses that we need
labels_raw <- read_file("gss_labels.txt")


#### Set-up the dictionary ####
# What we want is a variable name and a variable definition
variable_descriptions <- as_tibble(dict) %>% 
  filter(value!="}") %>% 
  mutate(value = str_replace(value, ".+%[0-9].*f[ ]{2,}", "")) %>% 
  mutate(value = str_remove_all(value, "\"")) %>% 
  rename(variable_description = value) %>% 
  bind_cols(tibble(variable_name = colnames(raw_data)[-1]))
 
# Now we want a variable name and the possible values
labels_raw_tibble <- as_tibble(str_split(labels_raw, ";")[[1]]) %>% 
  filter(row_number()!=1) %>% 
  mutate(value = str_remove(value, "\nlabel define ")) %>% 
  mutate(value = str_replace(value, "[ ]{2,}", "XXX")) %>% 
  mutate(splits = str_split(value, "XXX")) %>% 
  rowwise() %>% 
  mutate(variable_name = splits[1], cases = splits[2]) %>% 
  mutate(cases = str_replace_all(cases, "\n [ ]{2,}", "")) %>%
  select(variable_name, cases) %>% 
  drop_na()

# Now we have the variable name and the different options e.g. age and 0-9, 10-19, etc.
labels_raw_tibble <- labels_raw_tibble %>% 
  mutate(splits = str_split(cases, "[ ]{0,}\"[ ]{0,}"))

# The function sets up the regex (I know, I know, but eh: https://xkcd.com/208/)
add_cw_text <- function(x, y){
  if(!is.na(as.numeric(x))){
    x_new <- paste0(y, "==", x,"~")
  }
  else{
    x_new <- paste0("\"",x,"\",")
  }
  return(x_new)
}

# The function will be in the row, but it'll get the job done
cw_statements <- labels_raw_tibble %>% 
  rowwise() %>% 
  mutate(splits_with_cw_text = list(modify(splits, add_cw_text, y = variable_name))) %>% 
  mutate(cw_statement = paste(splits_with_cw_text, collapse = "")) %>% 
  mutate(cw_statement = paste0("case_when(", cw_statement,"TRUE~\"NA\")")) %>% 
  mutate(cw_statement = str_replace(cw_statement, ",\"\",",",")) %>% 
  select(variable_name, cw_statement)
# So for every variable we now have a case_when() statement that will convert 
# from the number to the actual response.

# Just do some finally cleanup of the regex.
cw_statements <- 
  cw_statements %>% 
  mutate(variable_name = str_remove_all(variable_name, "\\r")) %>% 
  mutate(cw_statement = str_remove_all(cw_statement, "\\r"))


#### Apply that dictionary to the raw data ####
# Pull out a bunch of variables and then apply the case when statement for the categorical variables
gss <- raw_data %>% 
  select(CASEID, 
         agedc, 
         achd_1c, 
         achdmpl, 
         totchdc, 
         acu0c,
         agema1c,
         achb1c,
         rsh_131a,
         arretwk,
         slm_01, 
         sex, 
         brthcan, 
         brthfcan,
         brthmcan,
         brthmacr,
         brthprvc,
         yrarri,
         prv, 
         region, 
         luc_rst, 
         marstat, 
         amb_01, 
         vismin, 
         alndimmg,
         bpr_16, 
         bpr_19,
         ehg3_01b, 
         odr_10, 
         livarr12, 
         dwelc, 
         hsdsizec,
         brthpcan,
         brtpprvc, 
         visminpr,
         rsh_125a, 
         eop_200,
         uhw_16gr,
         lmam_01, 
         acmpryr,
         srh_110,
         srh_115,
         religflg, 
         rlr_110,
         lanhome, 
         lan_01,
         famincg2, 
         ttlincg2, 
         noc1610, 
         cc_20_1,
         cc_30_1,
         ccmoc1c,
         cor_031,
         cor_041,
         cu0rnkc,
         pr_cl,
         chh0014c,
         nochricc,
         grndpa,
         gparliv,
         evermar,
         ma0_220,
         nmarevrc,
         ree_02,
         rsh_131b,
         rto_101,
         rto_110,
         rto_120,
         rtw_300,
         sts_410,
         csp_105,
         csp_110a,
         csp_110b,
         csp_110c,
         csp_110d,
         csp_160,
         fi_110) %>% 
  mutate_at(vars(agedc:fi_110), .funs = funs(ifelse(.>=96, NA, .))) %>% 
  mutate_at(.vars = vars(sex:fi_110),
            .funs = funs(eval(parse(text = cw_statements %>%
                                      filter(variable_name==deparse(substitute(.))) %>%
                                      select(cw_statement) %>%
                                      pull()))))

# Fix the names
gss <- gss %>% 
  clean_names() %>% 
  rename(age = agedc,
         age_first_child = achd_1c,
         age_youngest_child_under_6 = achdmpl,
         total_children = totchdc,
         age_start_relationship = acu0c,
         age_at_first_marriage = agema1c,
         age_at_first_birth = achb1c,
         distance_between_houses = rsh_131a,
         age_youngest_child_returned_work = arretwk,
         feelings_life = slm_01,
         sex = sex,
         place_birth_canada = brthcan,
         place_birth_father = brthfcan,
         place_birth_mother = brthmcan,
         place_birth_macro_region = brthmacr,
         place_birth_province = brthprvc,
         year_arrived_canada = yrarri,
         province = prv,
         region = region,
         pop_center = luc_rst,
         marital_status = marstat,
         aboriginal = amb_01,
         vis_minority = vismin,
         age_immigration = alndimmg,
         landed_immigrant = bpr_16,
         citizenship_status = bpr_19,
         education = ehg3_01b,
         own_rent = odr_10,
         living_arrangement = livarr12,
         hh_type = dwelc,
         hh_size = hsdsizec,
         partner_birth_country = brthpcan,
         partner_birth_province = brtpprvc,
         partner_vis_minority = visminpr,
         partner_sex = rsh_125a,
         partner_education = eop_200,
         average_hours_worked = uhw_16gr,
         worked_last_week = lmam_01,
         partner_main_activity = acmpryr,
         self_rated_health = srh_110,
         self_rated_mental_health = srh_115,
         religion_has_affiliation = religflg,
         regilion_importance = rlr_110,
         language_home = lanhome,
         language_knowledge = lan_01,
         income_family = famincg2,
         income_respondent = ttlincg2,
         occupation = noc1610,
         childcare_regular = cc_20_1,
         childcare_type = cc_30_1,
         childcare_monthly_cost = ccmoc1c,
         ever_fathered_child = cor_031,
         ever_given_birth = cor_041,
         number_of_current_union = cu0rnkc,
         lives_with_partner = pr_cl,
         children_in_household = chh0014c,
         number_total_children_intention = nochricc,
         has_grandchildren = grndpa,
         grandparents_still_living = gparliv,
         ever_married = evermar,
         current_marriage_is_first = ma0_220,
         number_marriages = nmarevrc,
         religion_participation = ree_02,
         partner_location_residence = rsh_131b,
         full_part_time_work = rto_101,
         time_off_work_birth = rto_110,
         reason_no_time_off_birth = rto_120,
         returned_same_job = rtw_300,
         satisfied_time_children = sts_410,
         provide_or_receive_fin_supp = csp_105,
         fin_supp_child_supp = csp_110a,
         fin_supp_child_exp = csp_110b,
         fin_supp_lump = csp_110c,
         fin_supp_other = csp_110d,
         fin_supp_agreement = csp_160,
         future_children_intention = fi_110) 

#### Clean up ####
gss <- gss %>% 
  mutate_at(vars(age:future_children_intention), 
            .funs = funs(ifelse(.=="Valid skip"|.=="Refusal"|.=="Not stated", "NA", .))) 

gss <- gss %>% 
  mutate(is_male = ifelse(sex=="Male", 1, 0)) 

gss <- gss %>% 
  mutate_at(vars(fin_supp_child_supp:fin_supp_other), .funs = funs(case_when(
    .=="Yes"~1,
    .=="No"~0,
    .=="NA"~as.numeric(NA)
  )))

main_act <- raw_data %>% 
  mutate(main_activity = case_when(
    mpl_105a=="Yes"~ "Working at a paid job/business",
    mpl_105b=="Yes" ~ "Looking for paid work",
    mpl_105c=="Yes" ~ "Going to school",
    mpl_105d=="Yes" ~ "Caring for children",
    mpl_105e=="Yes" ~ "Household work", 
    mpl_105i=="Yes" ~ "Other", 
    TRUE~ "NA")) %>% 
  select(main_activity) %>% 
  pull()

age_diff <- raw_data %>% 
  select(marstat, aprcu0c, adfgrma0) %>% 
  mutate_at(.vars = vars(aprcu0c:adfgrma0),
            .funs = funs(eval(parse(text = cw_statements %>%
                                      filter(variable_name==deparse(substitute(.))) %>%
                                      select(cw_statement) %>%
                                      pull())))) %>% 
  mutate(age_diff = ifelse(marstat=="Living common-law", aprcu0c, adfgrma0)) %>% 
  mutate_at(vars(age_diff), .funs = funs(ifelse(.=="Valid skip"|.=="Refusal"|.=="Not stated", "NA", .))) %>% 
  select(age_diff) %>% 
  pull()

gss <- gss %>% mutate(main_activity = main_act, age_diff = age_diff)

# Change some from strings into numbers
gss <- gss %>% 
  rowwise() %>% 
  mutate(hh_size = str_remove(string = hh_size, pattern = "\\ .*")) %>% 
  mutate(hh_size = case_when(
    hh_size=="One" ~ 1,
    hh_size=="Two" ~ 2,
    hh_size=="Three" ~ 3,
    hh_size=="Four" ~ 4,
    hh_size=="Five" ~ 5,
    hh_size=="Six" ~ 6
  )) 

gss <- gss %>% 
  rowwise() %>% 
  mutate(number_marriages = str_remove(string = number_marriages, pattern = "\\ .*")) %>% 
  mutate(number_marriages = case_when(
    number_marriages=="No" ~ 0,
    number_marriages=="One" ~ 1,
    number_marriages=="Two" ~ 2,
    number_marriages=="Three" ~ 3,
    number_marriages=="Four" ~ 4
  )) 

gss <- gss %>% 
  rowwise() %>% 
  mutate(number_total_children_known = ifelse(number_total_children_intention=="Don't know"|number_total_children_intention=="NA", 0, 1)) %>% 
  mutate(number_total_children_intention = str_remove(string = number_total_children_intention, pattern = "\\ .*")) %>% 
  mutate(number_total_children_intention = case_when(
    number_total_children_intention=="None" ~ 0,
    number_total_children_intention=="One" ~ 1,
    number_total_children_intention=="Two" ~ 2,
    number_total_children_intention=="Three" ~ 3,
    number_total_children_intention=="Four" ~ 4,
    number_total_children_intention=="Don't" ~ as.numeric(NA)
  )) 

write_csv(gss, "gss.csv")

```


```{r, eval = TRUE, echo=TRUE}

GSS_Group %>% kable(caption = "Proportion of Population in Each Cell (Full Table)")

```

